---
title: "Machine Learning with {tidymodels}"
author:
- name: Emil Hvitfeldt
  url: https://www.emilhvitfeldt.com/
  affiliation: Teladoc Health
  affiliation_url: https://www.teladochealth.com/
  orcid_id: 0000-0002-0679-1945
date: "2021-11-02"
description: |
  1 day workshop at NHS-R Conference – 2021
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r meta, echo=FALSE}
library(metathis)
meta() %>%
 meta_general(
   description = "Machine Learning with {tidymodels}",
   generator = "xaringan and remark.js"
 ) %>%
 meta_name("github-repo" = "EmilHvitfeldt/nhs-tidymodels-workshop") %>%
 meta_social(
   title = "Machine Learning with {tidymodels}",
   url = "https://nhs-tidymodels-workshop.netlify.app/",
   og_type = "website",
   twitter_card_type = "summary_large_image"
 )
```

## Welcome  

Summary: This workshop will provide a gentle introduction to machine learning with R using the modern suite of predictive modeling packages called {tidymodels}.
We will build, evaluate, compare, and tune predictive models. Along the way, we’ll learn about key concepts in machine learning including overfitting, the holdout method, the bias-variance trade-off, ensembling, cross-validation, and feature engineering.
Learners will gain knowledge about good predictive modeling practices, as well as hands-on experience using {tidymodels} packages like {parsnip}, {rsample}, {recipes}, {yardstick}, and {tune}.

Pre-requisites: Some introductory experience with R.

## Slides

+ [1: Introduction](1-introduction.html)
+ [2: Models](2-models.html)
+ [3: Features](3-features.html)
+ [4: Resampling](4-resampling.html)
+ [5: Tuning](5-tuning.html)

## Labs

Link to lab for local download [here](static/labs.Rmd)

## Links

+ Link to tidymodels main website <https://www.tidymodels.org/>

+ Link to "Tidy Modeling with R" book: <https://www.tmwr.org/>

## Acknowledgments {.appendix}

This is website made with the [distill package](https://rstudio.github.io/distill/).
